% E. Dunham -- Resume
% Contents Copyright (C) 2014 - 2015, E. Dunham

% LaTeX code for rendering the resume is distributed under the MIT license.
% See LICENSE.txt. It means you can use the code for whatever you want,
% including your own resume, but I'm not liable if it catches your computer on
% fire.

% Template originally developed by E. Dunham
% https://github.com/edunham/resume/blob/master/resume.tex

\documentclass[11pt]{article} % Set default font size to 11pt
\usepackage[normalem]{ulem} % for the underlines
\usepackage[compact]{titlesec} % Shrink default spacings
\usepackage{tabto} % For aligning skills section
\usepackage{hyperref}

\textwidth=7in
\textheight=10.5in
\topmargin -1.25in % Reclaim the default whitespace from top of page
\oddsidemargin -.25in % Reclaim whitespace on left, make it look centered
\pagenumbering{gobble} % Don't number pages
\setlength{\parindent}{0pt} % Don't indent paragraphs
\newcommand{\heading}[1]{
	%\section*{\centering\uline{\hfill #1 \hfill }} % Center the headings
	\section*{\uline{\hfill #1 }} % Right-align the headings
}
\newcommand{\squish}{
    \setlength{\itemsep}{0.2pt}
    \setlength{\parskip}{0pt} % tweak parskip value to adjust total height
    \setlength{\parsep}{0.2pt}
}
\newcommand{\when}[1]{ % naming this 'date' would conflict with builtins
    \hfill \texttt{#1}
}
\newcommand{\experience}[3]{ % place, optional title, date
    \ifx&#2&
        \item[{#1}]
    \else
        \item[{#1}, \emph{#2}]
    \fi
    \when{#3}
}
\newcommand{\contact}[3]{
    \centerline{ \large \texttt{#1} $\bullet$ \texttt{#2} $\bullet$ \emph{#3} }
}
\newcommand{\skill}[2]{
    \textbf{#1} \tabto{2.5in} #2
}
% Write C++ all fancy-like
% http://www.parashift.com/c++-faq-lite/latex-macros.html
\newcommand{\CPP}{
    C\hspace{-.05em}\raisebox{.4ex}{\tiny\bf +}\hspace{-.10em}\raisebox{.4ex}{\tiny\bf +}
}

\begin{document}

\centerline{{\huge \bf Bheesham Persaud}}
\bigskip

\contact{me@bheesham.com}
        {(613) 612 - 5847}
        {Ottawa, Canada}

\heading{Skills}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\skill{Systems Administration}
      {GNU/Linux (CentOS, Ubuntu), Docker, ZooKeeper, Buildbot, SSH}

\skill{Development}
      {C, \CPP, C\#, Rust, Clojure, Python, PHP, HTML/CSS/JavaScript}

\skill{Collaboration}
      {IRC, Git, Atlassian Jira \& Confluence}

%\skill{Robotics}
%      {Mechanical design \& prototyping, 3D modeling, OpenCV, Arduino}

\heading{Employment}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish
\experience{CENX}
           {Software Developer}
           {05/2016 - Present}

Developed OSS and LSO solutions for telecommunication companies using Clojure,
Datomic, Cassandra, Kafka, and Solr.

Improved tools that help emulate a customer's production environment on a
developer's laptop using Docker.

\experience{Shared Services Canada}
           {Developer / Analyst}
           {04/2015 - 01/2016}

Optimized programs that monitor the health and usage of large networks by
reducing disk I/O and redundant steps.

Created intranet websites which generate reports about network outages and
changes.

\experience{Carleton University}
           {Research Assistant}
           {05/2013 - 12/2014}

Researched gesture based authentication for Android and iOS.

Ported complex algorithms written in JavaScript to C/\CPP for use with the Java
Native Interface.

Researched increasing software diversity by creating permutations of the OpenSSL
library by using its forks: BoringSSL and LibreSSL.

\experience{Carleton Computer Science Society}
           {Director At Large: Services}
           {05/2012 - 05/2014}

Upgraded and maintained the different services the society ran on their Ubuntu
servers: DNS, HTTP.

\experience{Canadian Association of Physicists}
           {Web Developer}
           {01/2012 - 04/2013}

Maintained the Drupal website along with its many plugins and the Members only
area.

Fixed security flaws in legacy PHP and ASP systems.

Created new services to manage the release of magazines on a quarterly basis
using CodeIgniter (PHP).

\end{description}

\heading{Open-source Contributions}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish
\experience{Redox}
           {\url{https://www.redox-os.org}}
           {}

Contributed a patch which allowed the operating system to run on the x86-64 architecture.

\experience{xbps}
           {\url{http://www.voidlinux.eu/}}
           {}

Improved documentation for xbps, the package manager of the Void (Linux) distribution.

\experience{The Rust Programming Language}
           {\url{http://rust-lang.org/}}
           {}

Submitted minor improvements to the project's build scripts and documentation.

\experience{The Rust Project's Buildbot}
           {\url{http://buildbot.rust-lang.org/}}
           {}

Configured Buildbot to sign all release builds automatically and added basic authentication to the instance.
\end{description}

\heading{Academics}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish
\experience{Carleton University}
           {}
           {09/2011 - 02/2017}

           Bachelor of Computer Science: Computer \& Internet Security Stream, Honours \\
           \textbf{Thesis}: FrankenSSL: Recombining Cryptographic Libraries to Create Software Variants \\
           \textbf{Supervisor}: Anil Somayaji

\end{description}

\heading{Publications}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish
\experience{}
           {}
           {08/2016}

B. Persaud, B. Obada-Obieh, N. Mansourzadeh, A. Moni, and A. Somayaji.
FrankenSSL: Recombining Cryptographic Libraries for Software Diversity.
\textit{Proceedings of the 11th Annual Symposium On Information Assurance}.

\end{description}

\end{document}
